### 2016-06-01 sec1_introduction.tex
Updated Introduction charts
need to simplify part of the introduction

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving patterns 
with different constraints in the attributes of clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

>>>>

Table~\ref{tbl:existing_co_patterns} summarizes several popular co-moving pattern s 
with different constraints in the attributes of clustering in spatial proximity,
consecutiveness in temporal duration and computational complexity. 
In particular,  the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{group}~\cite{wang2006grouppattern} patterns require 
all the objects in a group to be enclosed by a disk with radius $r$; 
whereas the \emph{convoy}~\cite{jeung2008convoy}, the \emph{swarm}~\cite{li2010swarm} 
and the \emph{platoon}~\cite{li2015platoon} patterns resort to density-based 
spatial clustering. 
In the temporal dimension, the \emph{flock}~\cite{gudmundsson2006flock} 
and the \emph{convoy}~\cite{jeung2008convoy} require all the timestamps 
of each detected spatial group to be consecutive, which is referred to as \emph{global consecutiveness}; 
whereas the \emph{swarm}~\cite{li2010swarm} does not impose any restriction. 
The \emph{group}~\cite{wang2006grouppattern} and the \emph{platoon}~\cite{li2015platoon} adopt a compromised manner by allowing
arbitrary gaps between the consecutive segments, which is called \emph{local consecutiveness}. 
They introduce a parameter $L$ to control the minimum length of each local consecutive segment.

### 2016-06-01 sec7_optimization.tex
Updated Introduction charts
need to simplify part of the introduction

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with degree $d$ and $n$ vertexes.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For any numbering, $\mathbb{A}$, with high probability, the 
absolute difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
for each object, by the pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be a 0-1 indicator variable determining whether vertex $i$ connects vertex $j$
in $G$. Note that edges in $G$ are independent. We use $d_i$ 
to denote the degree of object $i$ in $G$.  It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the ending vertex
with lower ID, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

@@

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1\leq j \leq n}(c_j) > \mu + t)$ can be viewed as
$\cup_{c_i} (c_i > \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty > \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) > \mu + t)  \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty > (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
equation holds:
\begin{equation*}
Pr(||A\vec{b}||_\infty > (d/2 + O(\sqrt{d\log n})) \leq 1/n
\end{equation*}

>>>>

\begin{theorem}[Balance of Star Partition]
Let $G$ be a connection graph with $n$ vertexes and the average degree $d$.
Let $\mathbb{A}^*$ be the optimal numbering wrt. Equation 1.
For any numbering, $\mathbb{A}$, with high probability, the 
absolute difference between $\mathbb{A}^*$ and $\mathbb{A}$ is $O(\sqrt{n \log n})$.
That is, it is very likely that 
$||\mathbb{A}\vec{b}||_\infty = ||\mathbb{A}^*\vec{b}||_\infty + O(\sqrt{n \log n})$.
\end{theorem}

\begin{proof}
Let $\mathbb{A}^*$ be the optimal solution wrt Equation 1. Since we have a star
for each object, by the degree-sum formula and pigeon-hole theorem, $||A^*\vec{b}||_\infty \geq d/2$.
Next, let $e_{i,j}$ be a 0-1 indicator variable determining whether vertex $i$ connects vertex $j$
in $G$. Note that edges in $G$ are independent. We use $d_i$ 
to denote the degree of object $i$ in $G$.  It follows that $E[d_i]=E[\Sigma_{1\leq j \leq n}e_{i,j}]=d$.
Since in the star partition, each edge is assigned to the ending vertex
with lower ID, the connection between $a_{i,j}$ and $e_{i,j}$ can be written as:
\begin{equation*}
a_{i,j} = \begin{cases}
			e_{i,j}, i>j \\
			0, otherwise
		  \end{cases}  
\end{equation*}
There are two observations made on the above equation. First, since $e_{i,j}$s are independent,
$a_{i,j}$s are independent. Second, since $i>j$ and $e_{i,j}$ are independent. 
$E[a_{i,j}] = E[e_{i,j}]E[i>j]= E[e_{i,j}]/2$.

@@

The first step is due to the fact that all $a_{i,j}$ are bounded in the range of [0,1]. 
Next, since the event $(\max_{1\leq j \leq n}(c_j) \geq \mu + t)$ can be viewed as
$\cup_{c_i} (c_i \geq \mu + t )$, by Union Bound, we achieve the following:
\begin{equation*}
\begin{split}
	Pr(||A\vec{b}||_\infty \geq \mu + t) &=Pr(\max_{1\leq j \leq n}(c_j) \geq \mu + t)  \\
		& = Pr(\cup_{c_i} (c_i \geq \mu + t )) \\
		&\leq \Sigma_{1 \leq i \leq n} Pr(c_i \geq \mu + t) \\
		& = n^{-1} = 1/n
\end{split}
\end{equation*}
Substitute $t$ and $\mu$, we achieve the following concise form:
\begin{equation*}
	Pr(||A\vec{b}||_\infty \geq (d/2 + \sqrt{n\log n})) \leq 1/n
\end{equation*}
This indicates that, the probability of $(||A\vec{b}||_\infty-d/2)$ being less than or equal to $ O(\sqrt{n\log n})$ is $(1-1/n)$. With the observed fact that $||A^*\vec{b}||_\infty \geq d/2$, we conclude that
with probability greater than $(1-1/n)$, 
the difference between $||A\vec{b}||_\infty$ and $||A^*\vec{b}||_\infty$ is less than $O(\sqrt{n\log n})$.
\end{proof}

In fact, we have a tighter bound of $||A\vec{b}||_\infty -||A^*\vec{b}||_\infty$ if 
the connection graph is \emph{dense}. Specifically, if $d\geq \sqrt{12\log n}$, the following
equation holds:
\begin{equation*}
Pr(||A\vec{b}||_\infty \geq (d/2 + O(\sqrt{d\log n})) \leq 1/n
\end{equation*}
